Example Manuscript Template for a Data Analysis Project

### 2025-03-24 products/manuscript/Manuscript.qmd
commit all changes to these files
commit to the changes made on the manuscript and the
code

* First Autor$^{1,2,*}$ (ORCID: 0000-0000-1234-5678) 
* Second Author$^{3, *}$
* Third Autor$^{3, \dagger}$
* Last Author$^{1, 2, \land}$

@@

Proposed Analysis Method

@@

Mycobacterium tuberculosis infection is acquired mostly through sharing air space with an individual who has active tuberculosis and inhaling droplet aerosols produced by that person. Since this bacterium is transmitted via the respiratory route to susceptible individuals in the community, the household of an infectious person is an environment for intense transmission of M. tuberculosis where most new cases of infection and diseases might be detected and treated. 
According some reports,they suggest that there are differences in the  responses to tuberculosis between men and women. These reports highlight greater barrier to early detection and treatment of tuberculosis to be greater for women than men.

The World Health Organisations, among others, attributed to the differences in the tuberculosis trends between men and women to access to care and treatment, pregnancy effects and gender rules that diminish the social capital of women hence lowering incidence among them[@CCWhalen2023]. Not forgetting that biological mechanisms might influence these differences,  previous studies show that men have a higher incidence and prevalence of disease and this might lead to bad treatment outcomes as compared to women.

Since the balance of fat and lean tissue differ in men and women especially at the time of presentation, the objective of this study will be to find out whether the more immune activation there is, the more infected / sicker is the person.

@@

This study utilized a cohort design analyzing data from 2021. We included all patients that were 15 years and older. The candidate must have had TB as their first episode, not on any hormonal therapy and does not take any hormonal birth control. The participant was not supposed to have diabetes melitus, cancer or HIV.Similarly,the exclusion criteria applied. All participants that were below the age of 15, reported TB as their second episode, took any form of hormanl therapy or biirth control , had diabetes melitus, cancer or HIV were excluded from the study.

The variables of interest were extracted from the TRAC dataset  and exported to an MS Excel sheet. The outcome variable was CD4+ immune activatin counts.  The primary independent variable was sex (cis-gender) and this was categorized as male and female. The covariates were age at diagnosis,BMI, Fat in Kg, lean body mass in kg(LBM in kg), CD4+ and CD4 immune activation counts.

>>>>

* First Autor$^{1,2,*}$ (ORCID: 0000-0000-1234-5678) 
* Second Author$^{3, *}$

@@

Proposed Analysis Method.

@@

Mycobacterium tuberculosis infection primarily spreads when a person shares airspace with someone who has active tuberculosis and inhales infectious droplet aerosols. Since the bacterium transmits through respiratory routes to susceptible individuals, the household of an infected person becomes a critical environment for intense M. tuberculosis transmission, where most new infections and cases can be detected and treated.
Research reports indicate significant differences in tuberculosis responses between men and women. Notably, these studies suggest that women face greater barriers to early detection and treatment of tuberculosis compared to men, potentially impacting disease outcomes and progression.

The World Health Organisations, among others, attributed to the differences in the tuberculosis trends between men and women to access to care and treatment, pregnancy effects,body fat mass and gender rules that diminish the social capital of women hence lowering incidence among them[@CCWhalen2023]. Not forgetting that biological mechanisms might influence these differences,  previous studies show that men have a higher incidence and prevalence of disease and this might lead to bad treatment outcomes as compared to women.

Body fat plays an important role in supporting immune function, and women typically maintain higher fat storage than men. This increased fat storage may contribute to women's stronger immune responses. Since the balance of fat and lean tissue differs significantly between men and women, particularly at the time of disease presentation, the objective of this study is to determine whether higher immune activation correlates with greater infection severity or illness.

@@

This study utilized a cross sectional study design analyzing data from 2017.Sixty TB-confirmed participants (30 males, 30 females, aged 15+) were recruited from Mulago Hospital.

\textbf{inclusion and exclusion critera}

Our study included patients aged 15 years and older who were experiencing their first episode of tuberculosis. To maintain data integrity, we excluded individuals who were receiving hormonal therapy or using hormonal contraceptives. Additionally, patients with comorbidities such as diabetes mellitus, cancer, or HIV were excluded from the study. Conversely, we applied strict exclusion criteria to ensure a focused research population: all individuals under 15 years of age, those with recurrent TB episodes, patients taking any form of hormonal therapy or contraception, and those diagnosed with diabetes mellitus, cancer, or HIV were not enrolled in the study.

The variables of interest were extracted from the TRAC dataset  and exported to an MS Excel sheet. The outcome variable was CD4+ immune activatin counts.  The primary independent variable was sex (cis-gender) and this was categorized as male and female. The covariates were age at diagnosis,BMI, Fat in Kg, lean body mass in kg(LBM in kg), CD4+ and CD4 immune activation counts. other variables  like fat mass index (FMI) and fat-free mass index (FFMI) were also obtained.
